### 2017-11-06 Draft2/Appending.Growth.tex
Use dfrac in a place or 2
Finish the space complexity section

Now, consider the ratio $\lim_{n \to \infty} \left( \FuncSpaceTail(\VarUseful) / \VarCapacitySeq_\VarUseful \right) = O(\log n) / O(n) = O({\log n} / {n}) = 0$. Because it is $0$, from \ref{thm:RemovesLowerOrderTerms} we may conclude
\begin{align*}
\FuncSpace(n) = \VarCapacitySeq_\VarUseful + \FuncSpaceTail(\VarUseful) \sim \VarCapacitySeq_\VarUseful
\end{align*}

% Bookmark

Using Lemma \ref{lem:VarUsefulIsOLogN} again, $\FuncSpaceTail(\VarUseful) = O(\VarUseful) = O(\log n)$. Similarly to before, the $\FuncSpaceTail(\VarUseful)$ term vanishes under $\sim$:
\begin{align*}
\FuncSpace(n) \sim ... + O(\log n) = ...
\end{align*}

>>>>

Now, consider the ratio $\lim_{n \to \infty} \dfrac {\FuncSpaceTail(\VarUseful)} {\VarCapacitySeq_\VarUseful} = \dfrac {O(\log n)} {O(n)} = O \left( \dfrac{\log n}{n} \right) = 0$. Because it is $0$, from Theorem \ref{thm:RemovesLowerOrderTerms} one can conclude
\begin{align*}
\FuncSpace(n) = \VarCapacitySeq_\VarUseful + \FuncSpaceTail(\VarUseful) \sim \VarCapacitySeq_\VarUseful
\end{align*}
Substituting $\FuncSpace(n)$ for $\VarCapacitySeq_\VarUseful$ in the previous inequality,
\begin{align*}
n \FluteLeq \FuncSpace(n) \FluteLess \VarGrowthFactor{n}
\end{align*}
